---
output:
  html_document: default
  pdf_document: default
---

```{r setup,  echo=FALSE, warning=F, message=F}
library("dplyr")
df_bound<-read.table("boundaries.txt", sep="\t", stringsAsFactors=F,header=T,comment.char="") 
df_bound_WB<-read.table("boundaries_WB.txt", sep="\t", stringsAsFactors=F,header=T,comment.char="") 
df_indicators<-read.table("indicators.txt", sep="\t", stringsAsFactors=F,header=T,comment.char="") 
df_varcomp<-read.table("varcomp.txt", sep="\t", stringsAsFactors=F,header=T,comment.char="") 
df_var<-read.table("variables.txt", sep="\t", stringsAsFactors=F,header=T,comment.char="") 

#include=FALSE,

test <- df_indicators %>%
  distinct(Water_type,Indicator) %>%
  left_join(mutate(distinct(df_bound,Indicator),OK=1),by="Indicator") %>%
  filter(is.na(OK)) %>% select(-OK)
  

test2 <- df_bound %>%
  distinct(Water_type,Indicator) %>%
  left_join(mutate(distinct(df_indicators,Indicator),OK=1),by="Indicator") %>%
  filter(is.na(OK)) %>% select(-OK)


test3 <- df_indicators %>%
  distinct(Water_type,Measurement) %>%
  left_join(mutate(distinct(df_varcomp,Water_type,Measurement),OK=1),by=c("Water_type","Measurement")) %>%
  filter(is.na(OK)) %>% select(-OK)


test4 <- df_varcomp %>%
  distinct(Water_type,Measurement) %>%
  left_join(mutate(distinct(df_indicators,Water_type,Measurement),OK=1),by=c("Water_type","Measurement")) %>%
  filter(is.na(OK)) %>% select(-OK)
```
## Testing consistency between indicator and measurement names in the Excel Sheets for shinyapp

### Indicators
Indicators included in "Indicator data" sheet which are not found in "Boundaries"
```{r test1,  echo=FALSE}
test
```
Indicators included in "Boundaries" sheet which are not found in "Indicator data"
```{r test2,  echo=FALSE}
test2
```
### Variance components
Measurements included in "Indicator data" sheet which are not found in "Varcomp"
```{r test3,  echo=FALSE}
test3
```
Measurements included in "Varcomp" sheet which are not found in "Indicator data"
```{r test4,  echo=FALSE}
test4
```

### Conclusions
Boundaries for which there is/are no corresponding indicator listed in the "Indicator data" Sheet or variance component information without a related indicator are not a problem.

Its more of a problem if there are indicators listed in "Indicator data" which do not have variance component information or boundary data. There are 2 river indicators for which this is the case: RiverTNsummer and RiverOxygenSummer.

There is a comment from JAC in "Indicator data" that RiverTNsummer is not implemented yet.

